Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-05 paper.tex
Revising SOM stuff
The main problem is that motivation is still missing. There are many comments and questions inserted by me that have not been answered. Please @amorag mainly, but also @7ossam81 take a look at them.

Basically, SOM consists of two layers; input layer and output layer (also known as Kohen layer). Input layer is fully connected with the Kohen layer which is usually a two dimensional grid of neurons (i.e. units). This means that every neuron is linked to every input in the input layer.

The learning process of SOM is an iterative process applied in two stages. First, the weights of the network are initialized randomly then the n-dimensional input vectors are presented to the network sequentially so the distance between the weights of the neurons and the inputs are computed using the simple Euclidean distance. In the second stage, the neuron which has the shortest distance with the presented input vector is updated along with its neighbor neurons. This neuron is called the best matching unit (BMU). The goal of the learning process is to minimize the neighborhood distance in the output clusters.

>>>>

Basically, SOM consists of two layers: input layer and output, also
known as Kohonen, layer. Input layer is fully connected with the 
Kohen layer which is usually a two dimensional grid of neurons
(i.e. units). This means that every neuron is linked to every input in
the input layer.

SOM follows an iterative process applied in two stages: First, the
weights of the network are initialized randomly then the n-dimensional
input vectors are presented to the network sequentially so the
distance between the weights of the neurons and the inputs are
computed using the simple Euclidean distance; in the second stage, the
neuron which has the shortest distance with the presented input vector
is updated along with its neighbor neurons. This neuron is called the
best matching unit (BMU). The goal of the learning process is to
minimize the neighborhood distance in the output clusters.
